### 2025-06-09 research-methods.qmd
20250609 - spurious correlations

Lastly, the association might be spurious.
It might just reflect random variation (i.e., chance), and that when tested on an independent sample, what appeared as an association in the original dataset may not hold when testing the association in a new dataset.

>>>>

Lastly, the association might be spurious (pure coincidence).
It might just reflect random variation (i.e., chance), and that when tested on an independent sample, what appeared as an association in the original dataset may not hold when testing the association in a new dataset.
@Vigen2024 provides a collection of spurious correlations: <https://www.tylervigen.com/spurious-correlations> (archived at <https://perma.cc/L443-JPRN>).
As @Vigen2024 notes, spurious correlations may be particularly common in the context of outliers (extreme values), a small sample size, and when performing data dredging (or *p*-hacking)—i.e., examining the associations among many, many variables.
